ms_supplementary

### 2018-02-12 man/ms_3_discussion.Rmd
update

>>>>

### OTRA COSA 
#### Climate and tree relationship 
Frase de resultados que tenemos que poner en discussion: 
Precipitation of previous december was also positively correlated with tree growth in the northern population and in the highest location of the southern population. Hydrological, Spring and Summer SPEI showed a strong positive correlation with tree-growth (Figure 7b), specially for the northern population (r > 0.6), ... **which can be interpreted as higher sensitivity to drought of a drier site [@GeaIzquierdo2014]**.  
#### Disturbance
Estos periodos se relacionan bien con eventos antrópicos: mineria (el primero de ellos) y actividades forestales el segundo (esta frase de la minería y demás la dejamos para la discusión??).

### 2018-02-12 man/ms_figures.Rmd
update

# 
plot_rwi_crono <- ggplot(cro_rwi, aes(x=year, y=res)) +
  theme_bw() + 
  theme(panel.grid = element_blank(), 
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face="bold", size=12), 
        axis.text = element_text(face="bold", size=10), 
        axis.title = element_text(face="bold", size=12)) + 
  geom_hline(yintercept = 1, colour = "grey") + 
  geom_line(size=.8) + scale_y_continuous(breaks = seq(0.4,1.8, 0.2)) +
  facet_wrap(~site_sorted, scales = "fixed", ncol = 1,
             labeller = as_labeller(label_site)) + 
  ylab("Ring width index") + xlab("Year") + 
  geom_vline(xintercept = c(1995, 2005, 2012), linetype = "dotted") + 
  geom_vline(aes(xintercept = year), data = year_cutoffs,  linetype = "dashed", colour='red') + 
  geom_vline(aes(xintercept = year), data = year_sampledepth,  linetype = "dashed", colour='blue') +
  scale_x_continuous(limits = c(1819, 2016), 
                     breaks= seq(1820, 2020, by=20))

>>>>

cro_rwi <- cro_rwi %>% 
  mutate(siteF = case_when(
    site_sorted == "0_sj" ~ "Northern (SJ)",
    site_sorted == "1_caH" ~ "Southern High (Ca-High)",
    site_sorted == "2_caL" ~ "Southern Low (Ca-Low)"))

# 
plot_rwi_crono <- ggplot(cro_rwi, aes(x=year, y=res)) +
  theme_bw() + 
  theme(panel.grid = element_blank(), 
        strip.background = element_rect(fill = "white"),
        # strip.text = element_text(face="bold", size=12), 
        strip.text = element_blank(), 
        axis.text = element_text(face="bold", size=8), 
        axis.title = element_text(face="bold", size=12)) + 
  geom_hline(yintercept = 1, colour = "grey") + 
  geom_line(size=.8) + scale_y_continuous(breaks = seq(0.4,1.8, 0.2)) +
  facet_wrap(~site_sorted, scales = "free_x", ncol = 1,
             labeller = as_labeller(label_site)) + 
  ylab("Ring width index") + xlab("Year") + 
  geom_vline(xintercept = c(1995, 2005, 2012), linetype = "dotted") + 
  # geom_vline(aes(xintercept = year), data = year_cutoffs,  linetype = "dashed", colour='red') + 
  geom_vline(aes(xintercept = year), data = year_sampledepth,  linetype = "dashed", colour='blue') +
  scale_x_continuous(limits = c(1819, 2016), 
                     breaks= seq(1820, 2020, by=20)) +
  annotation_custom(x=1980, y = 1.6)

### 2018-02-12 man/ms_supp.Rmd
update

**Figure S1** Acumulated monthly precipitation during the hydrological year 2004-2005 (blue line) and 2011-2012 (red line). The boxplot representing the average from 1940-2015 period. Data from meteorological station Granada, Base Aérea (National Spanish Meteorological Services (AEMET)).

@@

```{r}
df <- read.csv(file='../out/anomalies/evi/percen_browing_greening.csv', header=TRUE)

@@

per_pixels_green <- df %>% 
  ggplot(aes(x=type, y=per, fill=as.factor(y))) + 
  geom_bar(stat='identity', position = "dodge") + 
  geom_text(aes(label = paste0(per, " %")), position=position_dodge(width=0.9), vjust= - 0.75) + 
  facet_wrap(~clu_pop2) + 
  theme_bw() + xlab('') + ylab('Frequency of pixels (%)') +
  theme(strip.background = element_rect(colour = "black", fill = "white")
        ) + theme_minimal() + labs(fill = 'Drought event') + scale_fill_manual(values = c("#DAA520", "#104E8B"))

>>>>

**Figure S1** Acumulated monthly precipitation during the hydrological year 2004-2005 (blue line) and 2011-2012 (red line). The boxplot representing the average from 1940-2015 period. Data from meteorological station Granada, Base Aérea (National Spanish Meteorological Services, AEMET).

@@

```{r}
df <- read.csv(file=here::here('/out/anomalies/evi' ,'percen_browing_greening.csv'), header=TRUE)

@@

per_pixels_green <- df %>% 
  ggplot(aes(x=type, y=per, fill=as.factor(y))) + 
  geom_bar(stat='identity', position = "dodge") + 
  geom_text(aes(label = paste0(per, " %")), position=position_dodge(width=0.9), hjust=-.1, size=3, angle = 90) + 
  facet_wrap(~clu_pop2) + 
  theme_bw() + xlab('') + ylab('Frequency of pixels (%)') +
  theme(strip.background = element_rect(colour = "black", fill = "white")
        ) + labs(fill = 'Drought event') + scale_fill_manual(values = c("#DAA520", "#104E8B")) +
  scale_y_continuous(expand=c(.1,0))
